Report on Late Winter2013 Production: Image Differencing

### 2013-03-26 W13report.tex
Reorganization of sections based on Jeff's preferred outline

\section{Introduction}

@@

@@

\subsubsection{Measurement {\bf RUSS}}

@@

\subsection{Simulations {\bf ANDYC}}

@@

\section{KernelCandidate Statistics}

\subsection{Mean Squared Error {\bf SIMON}}

@@

\subsection{Reduced $\chi^2$ {\bf SIMON}}

\subsection{Control Sample {\bf SIMON}}

\section{False Detection Rate}

@@

\section{False Detection Dependencies}

@@

For completeness, we note the median differences in the image plane at
the time of detection are 3--4 counts (or 0.2 sigma relative to the
empirical variance) for v6866601, 0.2 counts (sigma) for v6866602, and
less than 0.1 counts (sigma) for v6866603.

>>>>

\section{Production Scope and Goals}

@@

\section{Work Performed}

@@

\subsubsection{Improvements to Measurement {\bf RUSS}}

@@

\subsection{Image Simulations {\bf ANDYC}}

@@

\subsection{KernelCandidate Statistics}

\subsubsection{Mean Squared Error {\bf SIMON}}

@@

\subsubsection{Reduced $\chi^2$ {\bf SIMON}}

\subsubsection{Control Sample {\bf SIMON}}

\section{Results: False Detection Rate}

@@

\section{Results: False Detection Dependencies}

@@

For completeness, we note the median differences in the image plane at
the time of detection are 3--4 counts (or 0.2 sigma relative to the
empirical variance) for v6866601, 0.2 counts (0.02 sigma) for
v6866602, and less than 0.1 counts (sigma) for v6866603.

\section{Results: Computational Performance}

Uh...
